Model Fitting

### 2017-08-08 model fitting/model_fitting.Rmd
copied data file folder

```{r, include = FALSE}
#function to compare nested models 
compare_nested <- function(crfull, crreduced, param_full, param_reduced) {
  like_f <- crfull[[loglik]]
  like_r <- crreduced[[loglik]]
  stat <- 2*(like_f - like_r)
}
```

@@

>>>>

@@

```{r}
#function to compare nested models
#full and reduced = number of parameters 
compare_nested <- function(crfull, crreduced, full, reduced) {
  s_full <- summary(crfull)
  s_red <- summary(crreduced)
  like_f <- s_full[[loglik]]
  like_r <- s_red[[loglik]]
  stat <- 2*(like_f - like_r)
  df <- param_full - param_reduced
  pval <- 1 - pchisq(stat, df)
  return(stat, pval)
}

#reduced model
cr11_r <- coxph(Surv(time_until_answer, answered) ~ category + 
                 device_length + n_images + new_user + post_weekday + 
                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
                 title_questionmark + title_begin_wh + capital_text + 
                 capital_title + text_all_lower + prior_effort + update + 
                 newline_ratio, data = x)

#not calling loglik 
compare_nested("cr11", "cr11_r", full = 18, reduced = 17)
